Demo for a Quality of Service networking with Software Defined Network.

### 2017-03-15 report/paper.tex
ultima aggiunta

  The links on our network logically have many parameters in witch we can storage network's performance; in practice a NetworkX's graph support only 
  one or two link's attributes so we have create a lots of graphs with the same topological information but different link's attributes.

@@

\subsubsection{Delay}
Monitoring round-trip time provides important insights for network troubleshooting and traffic engineering.
The  common  monitoring  technique  is  to  actively  send  probe packets  from  selected  vantage  points  hosts  or  middleboxes.
In traditional  networks, the control over the network routing is
limited,  making  it  impossible  to  monitor  every  selected  path. The  emerging  concept  of  Software  Defined  Networking  simplifies
network  control.  However,  OpenFlow,  the  common  SDN protocol,   does   not   support   RTT   monitoring   as   part   of   its
specification. In this experience we have tryed to emply an tecnic to escape this problem\cite{rtt}.
\newline The idea is to measure the time that occure from sending a packet from controller to a switch and the time in which the packet return from
an other switch.
\\
\newline First we have to discovery round trip time from controller to every single switch on our topology.
In order to do this on the controller we start a timer, we send a proper packet to the switch specifing the \texttt{OFPP_CONTROLLER - Send to the controller}
option and when the message return to the controller we stop the timer and calculare RTT for the switch.
\begin{figure}[!h]
 \centering
 \includegraphics[scale=0.70]{images/rtt2.png}
 \caption{\emph{RTT between controller and OF switch}}
 \label{fig:topo}
\end{figure}
\newline
If we need to calculate the delay on a specific link, the rtt has to calculate with the headed switch of this link.
\\
\newline
Now we create a proper message with unique id. number, let's start a timer \texttt{TM1} and then send this message to a first switch specifing the output port.
Then when the packet comes to the second switch it identify the particular message and sends to the controller that stops it's dedicated timer \texttt{TM2}.
\newline This part required a particolar flow entry on the second switch in order to send to the controller only some particulare packet.
\begin{figure}[!h]
 \centering
 \includegraphics[scale=0.70]{images/rtt1.png}
 \caption{\emph{Pck from controller to itself following a particular way.}}
 \label{fig:topo}
\end{figure}
\\
\newline At this point we can calculate the delay of the link.
\\
\\
 delay = (TM2 - TM1) - RTT1/2 - RTT2/2
\\
\\
Teorethically this method must works but in practice there are a lot of delay introduced from computational congestion on the virtualized controller.
What we observe is a estimated delay like a few seconds which is not the case, infact if we made some \texttt{ping test} from one host to another host
in this SDN network we realize delay around 3ms.
\\

>>>>

  The links on our network logically have many parameters in witch we can storage network's performance; in practice a NetworkX's graph support only 
  one or two link's attributes so we have create a lots of graphs with the same topological information but different link's attributescd .

@@

\subsubsection{Delay}
Monitoring round-trip time provides important insights for network troubleshooting and traffic engineering.
The  common  monitoring  technique  is  to  actively  send  probe packets  from  selected  vantage  points  hosts  or  middleboxes.
In traditional  networks, the control over the network routing is
limited,  making  it  impossible  to  monitor  every  selected  path. The  emerging  concept  of  Software  Defined  Networking  simplifies
network  control.  However,  OpenFlow,  the  common  SDN protocol,   does   not   support   RTT   monitoring   as   part   of   its
specification. In this experience we have tryed to emply an tecnic to escape this problem\cite{rtt}.
\newline The idea is to measure the time that occure from sending a packet from controller to a switch and the time in which the packet return from
an other switch.
\\
\newline First we have to discovery round trip time from controller to every single switch on our topology.
In order to do this on the controller we start a timer, we send a proper packet to the switch specifing the \texttt{OFPP_CONTROLLER - Send to the controller}
option and when the message return to the controller we stop the timer and calculare RTT for the switch.
\begin{figure}[!h]
 \centering
 \includegraphics[scale=0.70]{images/rtt2.png}
 \caption{\emph{RTT between controller and OF switch}}
 \label{fig:topo}
\end{figure}
\newline
If we need to calculate the delay on a specific link, the rtt has to calculate with the headed switch of this link.
\\
\newline
Now we create a proper message with unique id. number, let's start a timer \texttt{TM1} and then send this message to a first switch specifing the output port.
Then when the packet comes to the second switch it identify the particular message and sends to the controller that stops it's dedicated timer \texttt{TM2}.
\newline This part required a particolar flow entry on the second switch in order to send to the controller only some particulare packet.
\begin{figure}[!h]
 \centering
 \includegraphics[scale=0.70]{images/rtt1.png}
 \caption{\emph{Pck from controller to itself following a particular way.}}
 \label{fig:topo}
\end{figure}
\\
\newline At this point we can calculate the delay of the link.
\\
\\
 delay = (TM2 - TM1) - RTT1/2 - RTT2/2
\\
\\
Teorethically this method must works but in practice there are a lot of delay introduced from computational congestion on the virtualized controller.
What we observe is a estimated delay like a few seconds which is not the case, infact if we made some \texttt{ping test} from one host to another host
in this SDN network we realize delay around 3ms.
\\
\\
The following picture shows the visual output that we can obtain from delay's graph. In this graph we storage only the core information;
\begin{figure}[!h]
 \centering
 \includegraphics[scale=0.26]{images/delay.png}
 \caption{\emph{Delay's graph.}}
 \label{fig:topo}
\end{figure}
